%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Senior Software Engineer} % Job title
{Botlabs GmbH} % Organization
{Berlin, Germany} % Location
{Jan. 2022 - Jan. 2024} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked on developing the KILT Blockchain (a polkadot parachain) and supporting infrastructure.}
\item {Responsible for chain maintenance of the substrate based node code and developing fullstack solutions on top of the chain.}
\item {API design and communications with the frontend teams.}
\item {Giving talks and workshops at conferences.}
\item {Techstack: rust, substrate, typescript, react, docker, kubernetes, postgresql}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Software Engineer} % Job title
{Contiamo GmbH} % Organization
{Berlin, Germany} % Location
{Dec. 2017 - Nov. 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked on a multi-tenant data catalog cloud platform.}
\item {Responsible for backend architecture of all components that supported the core functionality.}
\item {Lead engineer for resource management and search.}
\item {API design and communications with the frontend teams.}
\item {Techstack: golang, postgresql, docker, kubernetes, redis, gRPC, typescript, react}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software Engineer \& Architect} % Job title
{WebVariants GmbH} % Organization
{Magdeburg, Germany} % Location
{Nov. 2013 - Dec. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked on various projects for clients}
\item {Kraftzwerge, a decentralized energy storage and management platform where I designed and implemented a container based firmware for the smart energy meter}
\item {Lead architect and developer of SUSI, a c++ based extended event system targeting distributed embedded systems.}
\item {Frontend for commscope's ION-U distributed antenna system}
\item {VisuReal cloud platform for opticans}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Scientific assistent} % Job title
{Otto-von-Guericke University} % Organization
{Magdeburg, Germany} % Location
{Dec. 2011 - Okt. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented and simplified algorithms from unpublished papers.}
\item {Evaluated runtime characteristics and provided samples.}
\item {Worked on a framework for faster algorithm evaluation.}
\end{cvitems} 
}

%------------------------------------------------

\end{cventries}