%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Achievements and Open Source}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Technical Lead} % Affiliation/role
{Rareships DAO} % Organization/group
{zkSync Era} % Location
{Jan. 2023 - today} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Wrote and deployed the initial contracts for the Rareships DAO on exosama network.}
\item {Successfully performed a migration of the DAO to zkSync Era}
\item {A lot of fun and over 800 people are part of the DAOs community.}
\item {\url{https://rareships.games}}
\end{cvitems}
}%------------------------------------------------

%------------------------------------------------

\cventry
{Author} % Affiliation/role
{snake-os} % Organization/group
{a bootable x86 snake game in rust} % Location
{Dec. 2021} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Wrote a bootable x86 operating system that allows you to play snake.}
\item {The project is written in rust and heavily relies on crates and docs from the osdev community.}
\item {So far the project collected 330 stars on github.}
\end{cvitems}
}%------------------------------------------------

\cventry
{Author} % Affiliation/role
{host-device plugin} % Organization/group
{CNI (container network interfaces)} % Location
{May - Sep. 2017} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Wrote the host-device CNI plugin that can move any host network device into the network namespace of a container.}
\item {Initial use-case was to access a CAN-Bus from within a rkt container but now its used to support all kinds of otherwise unsupported network devices within k8s.}
\item {The plugin is deployed on every kubernetes node worldwide}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Author} % Affiliation/role
{SUSI was finalist for the embedded award} % Organization/group
{Embedded World Conference, Nürnberg, Germany} % Location
{2016} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {SUSI was nominated and made it to final round for the embedded award.}
\item {It is a c++ based extended event system targeting distributed embedded systems.}
\end{cvitems}
}

\end{cventries}